Supporting information

### 2019-08-20 supplementary_information.Rmd
Fix SLA units in SI

readd(table_dat) %>%
  select(-matches("area")) %>%
  kable(
    caption = table_cap_mass,
    format = "latex",
    col.names = linebreak(c(
      "PFT",
      "Leaf lifespan\n(months)",
      "SLA\n(kg m$^{-2}$)",
      "$N_\\textrm{mass}$\n(mg g$^{-1}$)",
      "$P_\\textrm{mass}$\n(mg g$^{-1}$)",
      "$R_\\textrm{d, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)",
      "$V_\\textrm{c, max, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)",
      "$J_\\textrm{max, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)"
    )),
    escape = FALSE,
    booktabs = TRUE
  ) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))

readd(table_dat) %>%
  select(-matches("mass")) %>%
  kable(
	caption = table_cap_area,
	format = "latex",
    col.names = linebreak(c(
      "PFT",
      "Leaf lifespan\n(months)",
      "SLA\n(kg m$^{-2}$)",
      "$N_\\textrm{area}$\n(g m$^{-2}$)",
      "$P_\\textrm{area}$\n(g m$^{-2}$)",
      "$R_\\textrm{d, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)",
      "$V_\\textrm{c, max, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)",
      "$J_\\textrm{max, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)"
    )),
	escape = FALSE,
	booktabs = TRUE
) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
```

>>>>

readd(table_dat) %>%
  select(-matches("area")) %>%
  kable(
    caption = table_cap_mass,
    format = "latex",
    col.names = linebreak(c(
      "PFT",
      "Leaf lifespan\n(months)",
      "SLA\n(m$^2$ kg$^{-1}$)",
      "$N_\\textrm{mass}$\n(mg g$^{-1}$)",
      "$P_\\textrm{mass}$\n(mg g$^{-1}$)",
      "$R_\\textrm{d, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)",
      "$V_\\textrm{c, max, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)",
      "$J_\\textrm{max, mass}$\n($\\mu$mol g$^{-1}$ s$^{-1}$)"
    )),
    escape = FALSE,
    booktabs = TRUE
  ) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))

readd(table_dat) %>%
  select(-matches("mass")) %>%
  kable(
	caption = table_cap_area,
	format = "latex",
    col.names = linebreak(c(
      "PFT",
      "Leaf lifespan\n(months)",
      "SLA\n(m$^2$ kg$^{-1}$)",
      "$N_\\textrm{area}$\n(g m$^{-2}$)",
      "$P_\\textrm{area}$\n(g m$^{-2}$)",
      "$R_\\textrm{d, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)",
      "$V_\\textrm{c, max, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)",
      "$J_\\textrm{max, area}$\n($\\mu$mol m$^{-2}$ s$^{-1}$)"
    )),
	escape = FALSE,
	booktabs = TRUE
) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
```
